\textbf{Appendix}\\ African Wild Dog Dispersal and Connectivity under Climate Change - Lessons Learned from Seasonal Flood Extremes

### 2023-03-14 Chapter_8/04_Manuscript/Manuscript_Support.tex
various updates
upd

%------------------------------------------------------------------------------
%	Titlepage: Header
%------------------------------------------------------------------------------
\title{\textbf{Appendix}\\ Flooding of the Okavango Delta influences
Connectivity for Dispersing African Wild Dogs}

% List of Authors
\author{
  David D. Hofmann\textsuperscript{1,2,\S} \orcid{0000-0003-3477-4365} \and
  Dominik M. Behr\textsuperscript{1,2} \orcid{0000-0001-7378-8538} \and
  John W. McNutt\textsuperscript{2} \and
  Arpat Ozgul\textsuperscript{1} \orcid{0000-0001-7477-2642} \and
  Gabriele Cozzi\textsuperscript{1,2} \orcid{0000-0002-1744-1940}
}

@@

%------------------------------------------------------------------------------
%  Appendix S1: Source-Specific Heatmaps
%------------------------------------------------------------------------------
\newpage
\section{Source-Specific Heatmaps}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_HeatmapsIndividual.png}
  \caption{}
  \label{Heatmaps}
  \end{center}
\end{figure}

%------------------------------------------------------------------------------
%  Appendix S2: Source-Specific Betweenness
%------------------------------------------------------------------------------
\newpage
\section{Source-Specific Betweenness}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_BetweennessIndividual.png}
  \caption{}
  \label{Betweenness}
  \end{center}
\end{figure}

%------------------------------------------------------------------------------
%  Appendix S3: Source-Specific Betweenness
%------------------------------------------------------------------------------
\newpage
\section{Source-Specific Inter-Patch Connectivity}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_IPCMain.png}
  \caption{}
  \label{IPCMain}
  \end{center}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_IPCBuffer.png}
  \caption{}
  \label{IPCBuffer}
  \end{center}
\end{figure}

\newpage
\begingroup
\singlespacing
\bibliography{Literatur}
\endgroup

>>>>

%------------------------------------------------------------------------------
%	Titlepage: Header
%------------------------------------------------------------------------------
\title{\textbf{Appendix}\\ African Wild Dog Dispersal and Connectivity under
Climate Change - Lessons Learned from Seasonal Flood Extremes}

% List of Authors
\author{
  David D. Hofmann\textsuperscript{1,2,\S} \orcid{0000-0003-3477-4365} \and
  Dominik M. Behr\textsuperscript{1,2} \orcid{0000-0001-7378-8538} \and
  John W. McNutt\textsuperscript{2} \and
  Arpat Ozgul\textsuperscript{1,2} \orcid{0000-0001-7477-2642} \and
  Gabriele Cozzi\textsuperscript{1,2} \orcid{0000-0002-1744-1940}
}

@@

\newpage
\section{Dispersal Model}
The model employed to simulate dispersal was based on an integrated step
selection function (iSSF). In (integrated) step selection functions (iSSFs,
\citealp{Fortin.2005, Avgar.2016}), observed GPS locations are converted into
steps (the straight-line traveled between two GPS recordings
\citep{Turchin.1998}) and compared to a set of \textit{random} steps in a
conditional logistic regression framework \citep{Fortin.2005, Thurfjell.2014,
Muff.2020, Fieberg.2021}. The model presented in \citep{Hofmann.2023} used
dispersal data collected on 16 dispersing AWDs from a free-ranging wild dog
population in northern Botswana. GPS data during dispersal was collected at
4-hourly intervals and translated into steps of similar duration. Observed steps
were then paired step with 24 random steps that were generated using a uniform
distribution for turning angles (\(-\pi, +\pi\)) and step lengths from a gamma
distribution fitted to observed steps (scale \(\theta\) = 6'308 and shape \(k\)
= 0.37). It was then assumed that animals assigned to each observed and random
step a selection score of the form \citep{Fortin.2005}:

\begin{equation}
\label{EQ1}
  w(x) = exp(\beta_1 x_1 + \beta_2 x_2 + ... + \beta_n x_n)
\end{equation}

Where (\(x_1, x_2, ..., x_n\)) represent the covariate values along each of the
steps and the (\(\beta_1, \beta_2, ..., \beta_n\)) are the animal's relative
selection strengths \citealp{Avgar.2017} towards these covariates. The benefit
of \textit{integrated} SSFs over regular SSFs is that they provide a means to
render two complementary ``kernels''. A \textit{movement} kernel that describes
general movement behavior of dispersing AWDs and a \textit{habitat} kernel that
describes preferences of AWDs with regards to environmental conditions
\citep{Fieberg.2021}. iSSFs also allow interactions among the two kernels and
are thus suitable to render that movement behavior may change depending on
habitat conditions. A fitted iSSF model can be used as an individual-based
movement model to simulate dispersal \citep{Signer.2017, Hofmann.2023}

\newpage
\section{Dispersal Model Estimates}
\Cref{Model} depicts the model estimates from \cite{Hofmann.2023} that we used
to simulate dispersal trajectories in this study.

\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_MovementModel.png}
  \caption{Model parameters from the step-selection model implemented by
  \cite{Hofmann.2023}. The model was fit to GPS data of dispersing African wild
  dogs and comprises of a habitat kernel (light blue band), a movement kernel
  (dark blue band), and their interactions (purple band). Abbreviations are as
  follows: sl = step-length, log(sl) = natural logarithm of the step-length,
  cos(ta) = cosine of the relative turning angle.}
  \label{Model}
  \end{center}
\end{figure}

\newpage
\section{Source-Specific Inter-Patch Connectivity}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_IPCMain.png}
  \caption{Spatial representation of inter-patch connectivity derived for each
  source-area separately across the two extreme flood-scenarios. The focal
  source area of each subfigure is highlighted by a red circle. Subfigure (a),
  for instance, depicts inter-patch connectivity for source-area 1.}
  \label{IPCMain}
  \end{center}
\end{figure}

\newpage
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_IPCBuffer.png}
  \caption{Spatial representation of emigration patterns derived for each
  source-area separately across the two extreme flood-scenarios. The focal
  source area of each subfigure is highlighted by a red circle. Subfigure (a),
  for instance, depicts the number of emigrating individuals from source-area
  1.}
  \label{IPCBuffer}
  \end{center}
\end{figure}

\newpage
\section{Source-Specific Heatmaps}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_HeatmapsIndividual.png}
  \caption{Heatmaps prepared for each source-area separately across the two
  extreme flood-scenarios. The focal source area of each subfigure is
  highlighted by a red circle. Subfigure (a), for instance, depicts the heatmaps
  for source-area 1.}
  \label{Heatmaps}
  \end{center}
\end{figure}

\newpage
\section{Source-Specific Betweenness}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_BetweennessIndividual.png}
  \caption{Betweenness maps prepared for each source-area separately across the
  two extreme flood-scenarios. The focal source area of each subfigure is
  highlighted by a red circle. Subfigure (a), for instance, depicts the
  betweenness maps for source-area 1.}
  \label{Betweenness}
  \end{center}
\end{figure}

\newpage
\section{Source-Specific Human Wildlife Conflict}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_HumanWildlifeConflictIndividual.png}
  \caption{Human wildlife conflict maps prepared for each source-area separately
  across the two extreme flood-scenarios. The focal source area of each
  subfigure is highlighted by a red circle. Subfigure (a), for instance, depicts
  the human wildlife conflict maps for source-area 1.}
  \label{HWC}
  \end{center}
\end{figure}

\newpage
\begingroup
\singlespacing
\bibliography{Literature}
\endgroup

### 2023-03-14 Chapter_8/04_Manuscript/Manuscript_Support_2023-01-19.tex
various updates

\textbf{Keywords:} movement, connectivity, climate change, seasonality,
dispersal, conservation, individual-based simulations, step-selection

@@

\newpage
\section{Dispersal Model Estimates}
\Cref{Model} depicts the model estimates from \cite{Hofmann.2023} that we used
to simulate dispersal trajectories in this study.

\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_MovementModel.png}
  \caption{Model parameters from the step-selection model implemented by
  \cite{Hofmann.2023}. The model was fit to GPS data of dispersing African wild
  dogs and comprises of a habitat kernel (light blue band), a movement kernel
  (dark blue band), and their interactions (purple band). Abbreviations are as
  follows: sl = step-length, log(sl) = natural logarithm of the step-length,
  cos(ta) = cosine of the relative turning angle.}
  \label{Model}
  \end{center}
\end{figure}

\newpage
\section{Source-Specific Inter-Patch Connectivity}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_IPCMain.png}
  \caption{Spatial representation of inter-patch connectivity derived for each
  source-area separately across the two extreme flood-scenarios. The focal
  source area of each subfigure is highlighted by a red circle. Subfigure (a),
  for instance, depicts inter-patch connectivity for source-area 1.}
  \label{IPCMain}
  \end{center}
\end{figure}

\newpage
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_IPCBuffer.png}
  \caption{Spatial representation of emigration patterns derived for each
  source-area separately across the two extreme flood-scenarios. The focal
  source area of each subfigure is highlighted by a red circle. Subfigure (a),
  for instance, depicts the number of emigrating individuals from source-area
  1.}
  \label{IPCBuffer}
  \end{center}
\end{figure}

\newpage
\section{Source-Specific Heatmaps}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_HeatmapsIndividual.png}
  \caption{Heatmaps prepared for each source-area separately across the two
  extreme flood-scenarios. The focal source area of each subfigure is
  highlighted by a red circle. Subfigure (a), for instance, depicts the heatmaps
  for source-area 1.}
  \label{Heatmaps}
  \end{center}
\end{figure}

\newpage
\section{Source-Specific Betweenness}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_BetweennessIndividual.png}
  \caption{Betweenness maps prepared for each source-area separately across the
  two extreme flood-scenarios. The focal source area of each subfigure is
  highlighted by a red circle. Subfigure (a), for instance, depicts the
  betweenness maps for source-area 1.}
  \label{Betweenness}
  \end{center}
\end{figure}

\newpage
\section{Source-Specific Human Wildlife Conflict}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_HumanWildlifeConflictIndividual.png}
  \caption{Human wildlife conflict maps prepared for each source-area separately
  across the two extreme flood-scenarios. The focal source area of each
  subfigure is highlighted by a red circle. Subfigure (a), for instance, depicts
  the human wildlife conflict maps for source-area 1.}
  \label{HWC}
  \end{center}
\end{figure}

\newpage
\begingroup
\singlespacing
\bibliography{Literature}
\endgroup

>>>>

\textbf{Keywords:} movement, connectivity, seasonality, dispersal, conservation,
permeability

@@

\newpage
\section{Source-Specific Heatmaps}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_HeatmapsIndividual.png}
  \caption{}
  \label{Heatmaps}
  \end{center}
\end{figure}

\newpage
\section{Source-Specific Betweenness}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_BetweennessIndividual.png}
  \caption{}
  \label{Betweenness}
  \end{center}
\end{figure}

\newpage
\section{Source-Specific Human Wildlife Conflict}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_HumanWildlifeConflictIndividual.png}
  \caption{}
  \label{HWC}
  \end{center}
\end{figure}

\newpage
\section{Source-Specific Inter-Patch Connectivity}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_IPCMain.png}
  \caption{Spatial representation of the tables 1a and 1b from the main
  manuscript.}
  \label{IPCMain}
  \end{center}
\end{figure}

\newpage
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = \textwidth]{99_IPCBuffer.png}
  \caption{}
  \label{IPCBuffer}
  \end{center}
\end{figure}

\newpage
\section{Emigration}
\begin{figure}[htbp]
  \begin{center}
  \includegraphics[width = 0.8\textwidth]{99_Emigration.png}
  \caption{Absolute number of simulated AWDs moving into each of the designated
  emigration zones (purple), in the minimum and maximum flood scenarios.}
  \label{Emigration}
  \end{center}
\end{figure}

\newpage
\begingroup
\singlespacing
\bibliography{Literatur}
\endgroup
